Sampling Bayesian probabilities given only sampled priors

### 2024-11-20 main.tex
Better hyperrank description

For the DES Y3 analyses, \citet{hyperrank} devised a scheme whereby the samples of \vecn\ are mapped into a small vector \vecu\ of summary statistics, such as their $\langle z \rangle,$  The \vecu\ space was effectively transformed into a new space $\mathcal{H}$ which is partitioned into regions of equal volume, each containing one sample.  The MC for the cosmology posterior samples over the continuous coordinates of $\mathcal{H}$ with a uniform prior, and the value of \vecn\ that ``owns'' the sampled point of $\mathcal{H}$ space is used to calculate to posterior. This method succeeds in defining a lower-dimensional nuisance space with simple (uniform) prior that yields equal probability to each of the original \vecn\ samples.  The result is, however, discontinuous in the $\mathcal{H}$-space parameters of the nuisance functions, which leads to very inefficient sampling of the posterior.  In particular, samplers such as \textsc{MultiNest} that assume continuity are rendered nearly non-functional.  As a result, the Y3 cosmological priors could not be evaluated with this method.  Instead, the \vecn\ samples were not used, and an \textit{ad hoc} $p(\vecn)$ was adopted which allowed only shifts and dilations of the mean $n(z)$ of the \vecn\ samples.

>>>>

For the DES Y3 analyses, \citet{hyperrank} devised a scheme whereby
the samples of \vecn\ are placed in a grid within some $M$-dimensional
unit hypercube $\mathcal{H}$.  The coordinates \vecu\ within the hypercube
are considered the compressed parameters of $n(z),$ and the
decompression function
$\hat{\vecn}(\vecu)$ outputs the $\vecn_\alpha$ sample at the nearest grid point to
  \vecu.  This solves the problem of creating a continuous \vecu\
  domain, and maintains the equal prior probability of each \vecn\
  sample, but the function \emph{output,} and the resultant likelihood
  function of \vecu\, are discontinuous.
Various strategies are proposed to assign the $\vecn_\alpha$ to the grid points in
$\mathcal{H}$ based on summary statistics, to reduce the
discontinuities.  But the function is never smooth.
As a consequence, many MC samplers become quite inefficient in
sampling of the cosmological posterior.  In particular, samplers such as \textsc{MultiNest} that assume continuity are rendered nearly non-functional.  As a result, the Y3 cosmological priors could not be evaluated with this method.  Instead, the \vecn\ samples were not used, and an \textit{ad hoc} $p(\vecn)$ was adopted which allowed only shifts and dilations of the mean $n(z)$ of the \vecn\ samples.
